LAGOS lake depth

### 2020-01-07 figures/01_geometry.Rmd
stash hypso panel source

ggplot(data = dt_raw) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("Normalized hypsography for ", length(unique(dt_raw$llid)), " lakes")) + 
  theme(legend.position = c(0.84, 0.2), 
        legend.title = element_blank()) +
  facet_wrap(~state)

>>>>

ggplot(data = dt_raw) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("Normalized hypsography", " (n=", length(unique(dt_raw$llid)), ") lakes")) + 
  theme(legend.position = c(0.84, 0.2), 
        legend.title = element_blank()) +
  facet_wrap(~state)
